Tabular Constraint Learning

### 2016-04-08 Paper/ECAI/tabular.tex
added the table

A \textit{vector} is either a column or a row that is type-consistent. If a vector is a row (column), we say that it has a \textit{row} (\textit{column}) orientation. A \textit{group} is a subrange of vectors with the same orientation in a table. We use the following notation to refer to a row (column) group $G$ in a table $T$ with rows (columns) ranging from $a$ to $b$: $G = T[a{:}b,:]$ ($G = T[{:},a{:}b]$), where $a,b$ are natural numbers.

An \textit{Excel constraint} is a triple \textit{(\CName, \CSignature, \CFunction)}, where \textit{\CName} is a textual name of the constraint; \textit{\CSignature} is a set of constraints specifying the properties of the arguments, such as their types, e.g., to require them to be integers or sizes, e.g. the length of vectors in the arguments must be equal, i.e., these are constraints on the group meta-information not on the actual group content; \textit{\CFunction} is a set of constraints specifying that the data in the subgroups satisfies the function. For example, an excel constraint \textit{rank} has \CName \textit{Y = RANK(X)}; its \CSignature is: $X$ is numeric, $Y$ is integer and the length of vectors in $X$ is the same as in $Y$; its \CFunction is the following constraint: a pair of vectors $x,y$ is a solution iff $x \in X, y \in Y$ and each value in $x$ has the rank (possibly with ties) specified in $y$.

@@

\subsection{Constraints}
The set of Excel constraints has a partial order in which they should be learned. For certain constraints this order does not matter, such as rank or product. For many others they have to be learned in the order, which is specified as a DAG in Figure \ref{fig:learning_order} \sergey{add the figure here}. This figure specifies a potential parallelization of the computation, since each connected component is independent of the others.

\begin{table}
  \centering
  \begin{tabular}{lcc}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\ 
  \end{tabular}
  \caption{Tabular Constraints}
  \label{table:constraints}
\end{table}

>>>>

A \textit{vector} is either a column or a row that is type-consistent. If a vector is a row (column), we say that it has a \textit{row} (\textit{column}) orientation. A \textit{group} is a subrange of vectors with the same orientation in a table. We use the following notation to refer to a row (column) group $G$ in a table $T$ with rows (columns) ranging from $a$ to $b$: $G = T[a{:}b,:]$ ($G = T[{:},a{:}b]$), where $a,b$ are natural numbers. We denote as the \textit{length} of a row (column) group $G$, written as \textit{length(G)}, the number of its columns (rows). We call a group $G$ \textit{numeric} (\textit{textual}, etc), written as \textit{numeric(G)}, if its vectors contain numeric (textual, etc) elements.

An \textit{Excel constraint} is a triple \textit{(\CName, \CSignature, \CFunction)}, where \textit{\CName} is a textual name of the constraint; \textit{\CSignature} is a set of constraints specifying the properties of the arguments, such as their types, e.g., to require them to be integers or sizes, e.g. the length of vectors in the arguments must be equal, i.e., these are constraints on the group meta-information not on the actual group content; \textit{\CFunction} is a set of constraints specifying that the data in the subgroups satisfies the function. For example, an excel constraint \textit{rank} has \CName \textit{Y = RANK(X)}; its \CSignature is: the group $G_X$ (associated with X) is numeric, $G_Y$ is integer and the length of vectors in $G_X$ is the same as in $G_Y$; its \CFunction is the following constraint: a pair of vectors $X,Y$ is a solution iff $X \in G_X, Y \in G_Y$ and each value in $X$ has the rank (possibly with ties) specified in $Y$.

@@

\subsection{Constraints}
The set of Excel constraints has a partial order in which they should be learned. For certain constraints this order does not matter, such as rank or product. For many others they have to be learned in the order, which is specified as a DAG in Figure \ref{fig:learning_order} (if a constraint is not in the graph, it is independent). This figure specifies a potential parallelization of the computation, since each connected component is independent of the others.

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.20\textwidth]{figures/constraint_dependency.png}
  \caption{Constraint Learning Order. The \textcolor{green}{solid} arrows indicate a construction order, i.e., learning one constraint is necessary to build the other. The \textcolor{red}{dashed} arrows indicate a pruning order, the former constraint is used to prune the latter.}
  \label{fig:learning_order}
\end{figure}

\newcommand{\numeric}{\format{numeric}}
\newcommand{\textual}{\format{textual}}
\newcommand{\integer}{\format{integer}}
\newcommand{\length}{\format{length}}
\newcommand{\nat}{\mathcal{N}}

\begin{table*}
  \centering
  \begin{tabular}{ccc}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\ 
    Y = RANK(X)     & $\numeric(G_X) \wedge \integer(G_Y) \wedge \length(G_X) = \length(G_Y)$ & $\begin{array}{r} X \in G_X, Y \in G_Y{:}~\forall i,j \in \nat{:}~(Y_i \leq Y_j \rightarrow X_{Y_i} \leq X_{Y_j}) \\ \wedge~ 1 \leq Y_i \leq \length(G_Y) \end{array}$ \\
    ALLDIFFERENT(X) & $\textual(G_X) \vee \integer(G_X) $ & $X \in G_X{:}~\forall i,j \in \nat{:}~i \neq j \rightarrow X[i] \neq X[j]$ \\
  \end{tabular}
  \caption{Excel Tabular Constraints \sergey{Luc, we need your comments here on the notation of $X,Y$ and $G_X,G_Y$}}
  \label{table:constraints}
\end{table*}
